\documentclass[a4paper,10pt]{article}
\usepackage{latexsym}
\usepackage[margin=0.85in]{geometry}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{hyperref}

\titleformat{\section}{\bfseries\large}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{10pt}{5pt}

\hypersetup{colorlinks=false}

\pagestyle{empty}
\setlist[itemize]{noitemsep, topsep=2pt, leftmargin=1.4em}
\setlength{\parskip}{0.3em}
\setlength{\parindent}{0pt}
\sloppy

\begin{document}

% ── Header ─────────────────────────────────────────────────────────────────
\begin{center}
    {\LARGE\bfseries Ashmit S Mukherjee} \\[0.3em]
    {\small New York University Abu Dhabi} \\[0.2em]
    \small
    \href{mailto:asm8879@nyu.edu}{asm8879@nyu.edu} \;\textbar\;
    \href{https://ashmitmukherjee.com}{ashmitmukherjee.com}
\end{center}

% ── Education ──────────────────────────────────────────────────────────────
\section*{Education}

\noindent\textbf{New York University Abu Dhabi} \hfill \textit{Expected May 2027} \\
B.S.\ in Computer Science \\
\textit{Studied at:} NYU Abu Dhabi; NYU Paris; NYU New York

\smallskip
\noindent\textbf{Relevant Coursework:} Natural Language Processing; Principles of Data Science;
Statistics for Social \& Behavioral Sciences; Data Structures \& Algorithms;
Computer Systems Architecture; Operating Systems

% ── Research Interests ─────────────────────────────────────────────────────
\section*{Research Interests}

I work at the intersection of machine learning and computational social science,
with a focus on how artificial agents affect cooperation, coordination, and norm
formation. My current work models social dilemmas in mixed human-AI populations
and asks when AI-mediated interventions support cooperation, and when they get in
the way. My broader work in multilingual NLP and protein representation learning
reflects the same methodological interest: how models learn structure from
heterogeneous data, and how we test that learning carefully.

% ── Publications ───────────────────────────────────────────────────────────
\section*{Publications}

\noindent
\textbf{A. Mukherjee} (co-first author).
``Bio-LoRA: Biological Priors as Inductive Bias for Low-Rank Adaptation.''
\textit{Under review at EMNLP 2026 Workshop}, 2026.

% ── Research Experience ────────────────────────────────────────────────────
\section*{Research Experience}

\noindent\textbf{Research Assistant: Human-AI Collaboration}, NYU Abu Dhabi
\hfill \textit{Feb 2026--Present}
\begin{itemize}
    \item Developing a simulation-based research platform for studying \textbf{AI-mediated
          coordination in multi-party social dilemmas}, using global supply chains as the
          domain (advisors: Prof.\ Hanan Salam, Prof.\ Benjamin Rosche).
    \item Built a calibrated game-theoretic environment with five buyers and three suppliers
          across repeated rounds, combining public goods support, strategic ignorance,
          threshold remediation, exit versus engagement, and auditing in one domain-grounded
          model. The main buyer policy uses quantal response equilibrium with a Stage 2 belief solver.
    \item Reproduced the target inefficient-equilibrium pattern, with about 22-26\% welfare
          loss versus the cooperative ceiling, about 99\% supplier defection, and about 7\%
          remediation across a 12-cell calibration sweep with 50 simulations per cell.
          The backend has 101 passing tests and three completed audit rounds.
    \item Designing the next phase as an experimental platform comparing algorithmic baselines
          against human-participant sessions in which AI agents act as advisors, coordinators,
          monitors, or commitment-support systems.
\end{itemize}

\vspace{0.3em}
\noindent\textbf{Research Assistant: eBRAIN Lab}, NYU Abu Dhabi
\hfill \textit{Jan 2026--Present}
\begin{itemize}
    \item Co-developed \textbf{Bio-LoRA}, a parameter-efficient fine-tuning method
          that injects residue-level biological priors (BLOSUM62, hydrophobicity, Grantham)
          into LoRA adapters for ESM-2 protein language models on signal peptide prediction.
    \item Showed BLOSUM62-guided LoRA matches or exceeds full fine-tuning on SignalP6
          benchmarks across SP MCC, cleavage-site exactness, and residue-level F1, while
          training only \textasciitilde3.6\% of parameters and using \textasciitilde43\% less
          peak GPU memory at the 3B-parameter scale.
    \item Designed multi-seed evaluation protocols and a one-factor sensitivity screen
          showing that single-seed improvements often fail to replicate, a methodological
          finding central to the paper's contribution.
    \item Manuscript under review (see Publications).
\end{itemize}

% ── Research Projects ──────────────────────────────────────────────────────
\section*{Research Projects}

\noindent\textbf{Hinglish Named Entity Recognition Benchmark} \hfill \textit{Fall 2024}
\begin{itemize}
    \item Fine-tuned multilingual transformer models, mBERT and XLM-RoBERTa, on the
          COMI-LINGUA dataset for Hindi-English code-mixed NER.
    \item Achieved 78\% entity-level F1, outperforming zero-shot GPT-4o and LLaMA 3.1
          baselines under controlled evaluation.
    \item Analyzed trade-offs between model scale, task-specific fine-tuning,
          generalization, and computational cost.
\end{itemize}

\vspace{0.3em}
\noindent\textbf{Data Science Salary Prediction Platform (Methodological Study)}
\hfill \textit{Fall 2025}
\begin{itemize}
    \item Conducted large-scale regression benchmarking using AutoML (PyCaret) across
          15+ models on a dataset of 3{,}000+ job postings.
    \item Analyzed feature contributions using SHAP to study labor market dynamics
          across geography, firm size, and skill requirements.
    \item Tracked experiments with MLflow; reported MAE, RMSE, and $R^2$ across conditions.
\end{itemize}

\vspace{0.3em}
\noindent\textbf{Crime Data Analysis and Prediction} \hfill \textit{Spring 2025}
\begin{itemize}
    \item Studied relationships between socioeconomic indicators and violent crime rates
          using regression modeling on data from 1{,}994 communities.
    \item Evaluated model performance via cross-validation ($R^2 = 0.85$) and exploratory
          statistical analysis; built interactive visualizations for interpretability.
\end{itemize}

\vspace{0.3em}
\noindent\textbf{CAMP: Campus Asset Management Platform} \hfill \textit{Fall 2024}
\begin{itemize}
    \item Designed and implemented a multi-user system for resource allocation and
          scheduling under shared constraints, including role-based access and conflict resolution.
    \item Developed RESTful APIs and automated CI/CD pipelines using Docker and
          GitHub Actions for reproducible deployment.
\end{itemize}

% ── Industry Experience ────────────────────────────────────────────────────
\section*{Industry Experience}

\noindent\textbf{Machine Learning Engineer Intern}, Zeek \hfill \textit{Jun--Aug 2025}
\begin{itemize}
    \item Developed and evaluated segmentation models on noisy real-world data,
          iterating on preprocessing and model selection for production reliability.
    \item Applied model interpretability techniques to study robustness and bias
          sensitivity, helping the team decide which model variants to deploy.
    \item Contributed to the team's evaluation workflow by adding standardized metrics
          and validation procedures to the model development cycle.
\end{itemize}

% ── Technical Skills ───────────────────────────────────────────────────────
\section*{Technical Skills}

\noindent
\textbf{Languages:} Python, C++, C\#, JavaScript \\
\textbf{ML \& NLP:} PyTorch, Transformers (Hugging Face), Scikit-Learn, XGBoost,
  PyCaret, SHAP \\
\textbf{Multi-Agent \& RL:} NumPy, NetworkX, reinforcement learning pipelines \\
\textbf{Data Analysis:} Pandas, SciPy, Matplotlib, Seaborn, Plotly \\
\textbf{Experiment Tracking:} MLflow, Git, Docker, GitHub Actions \\
\textbf{Other:} Streamlit, MongoDB, \LaTeX

\end{document}
